Holomorphic field theories and higher algebra

### 2022-11-14 draft.tex
random

@@

This theorem provides an elegant interpretation of BV quantization as a kind of deformation quantization. In the setting of mechanics (or one-dimensional field theory, since a particle has a worldline), deformation quantization explains the transition from classical to quantum as deforming the observables from a Poisson algebra to an associative algebra. 
This theorem allows one to interpret quantization of field theories---on manifolds of arbitrary dimension---as a deformation quantization from a 1-shifted Poisson factorization algebra to a plain factorization algebra.

>>>>

\subsubsection{Examples related to vertex algebras}

We have just recalled that in the complex dimension one case, holomorphic  polydiscs algebras (with a compatible $U(1)$ action) correspond to vertex algebras.
Let us briefly point out a few examples of this correspondence.

Given a Lie algebra $\lie{g}$ we obtain a one-dimensional holomorphic disc algebra $A_{\lie{g}}$ by the following construction. 
To a disk $D_r(z)$ of radius $r$ centered at $z \in \CC$ we attach the cochain complex
\beqn
A_{\lie{g}} (D_r(z)) = C_\bu \left(\lie{g} \otimes \Omega^{0,\bu}_c(D_r(z)) \right) 
\eeqn
Here, $\Omega^{0,\bu}_c(D_r(z))$ denotes the Dolbeault complex of compactly supported $(0,\bu)$ forms on the disc.
Because the space of $(0,\bu)$ forms define a commutative dg algebra, 
the complex $\lie{g} \otimes \Omega^{0,\bu}_c(D_r(z))$ has the natural structure of a dg Lie algebra---the complex on the right hand side is the Chevalley--Eilenberg complex which computes the Lie algebra homology of this dg Lie algebra.
Using the formalism of factorization algebras (which we recall in the next section) it is shown in \cite{CG2} how to equip $A_{\lie{g}}$ with the structure of a holomorphic disc algebra.
The corresponding vertex algebra is the Kac--Moody vertex algebra of $\fg$ at level zero. 
To obtain the vertex algebra associated to a nonzero level $\kappa$ one can deform this holomorphic polydisc algebra $A_{\fg} \rightsquigarrow A_{\fg, \kappa}$.

Let $V$ be a vector space.
Then, we can define a holomorphic disc algebra $A_V$ which corresponds to another familiar vertex algebra: the $\beta\gamma$ system with values in~$V$.
To a disc $D = D_r(z)$ this assigns the following cochain complex
\beqn
\Sym \left(\Omega^{1,\bu}_c(D) \otimes V^* [1] \oplus \Omega^{0,\bu}_c (D) \otimes V [1]\right) 
\eeqn
where the differential is $\dbar + \triangle$ which we will explain momentarily. 
We denote the linear generators of this symmetric algebra by $\gamma \in \Omega^{1,\bu}_c(D) \otimes V^* [1]$ and $\beta \in \Omega^{0,\bu}_c(D) \otimes V^* [1]$.
Now, for the differential, $\dbar$ is the familiar operator (which acts in the standard way on $(0,\bu)$ and $(1,\bu)$ forms) and $\triangle$ can be defined on $\Sym^2$ summand by the formula
\beqn
\triangle (\gamma \cdot \beta) = \int_D \<\gamma, \beta\> . 
\eeqn
The operator can be extended to the entire complex $A_V(D)$ by the rule that it is a BV operator for the $1$-shifted Poisson bracket given by wedge and integration.

@@

This theorem provides an elegant interpretation of BV quantization as a kind of deformation quantization. 
In the setting of mechanics (or one-dimensional field theory, since a particle has a worldline), deformation quantization explains the transition from classical to quantum as deforming the observables from a Poisson algebra to an associative algebra. 
This theorem allows one to interpret quantization of field theories---on manifolds of arbitrary dimension---as a deformation quantization from a 1-shifted Poisson factorization algebra to a plain factorization algebra. 
In fact, in \cite{GLL,Si Kai and Zhengping} it is shown how BV quantization for one-dimensional quantum field theories connects with the ordinary theory of deformation quantization.
